### 2020-11-15 thesis/thesis.tex
update for last comments

@@

Connectivity conservation planning (CCP), refers to the enterprise that engages multiple actors such as academics, NGOs (Non-Governmental Organizations), governmental bodies at different scales and in a common goal to conserve and restore the ecological connectivity of the landscape. CCP methods usually involve modelling the connectivity of the landscape of interest and using a prioritization method to determine conservation priorities, and modify land use practices to conserve or improve connectivity. This thesis  contributes to an ongoing CCP in Montérégie, in southern Québec. In the following, we introduce connectivity modelling. We then introduce the study region and describe previous CCP and research. We point out ways in which CCP methods can be improved and how this thesis contributes to doing so. We then introduce the two other key concepts of the thesis: land use change modelling and participatory methods. \\ \vspace{2em}

@@

In this thesis, we attempt to remedy those two limitations. In the first chapter, we combined a connectivity model using circuit theory with a land use and climate change model that uses a combination of statistical modelling and MCMC-based simulations. In the second chapter, we ran a stakeholder workshop to derive conservation priorities and use those results as inputs to derive simple, community driven, alternative conservation scenarios. We compare and contrast the results of these scenarios, and discuss the importance of considering stakeholder inputs to produce a resilient network of protected areas. \\

@@

This thesis therefore makes use of a hybrid modeling approach. We combine this model with scenarios which were derived from participatory methods. Next we introduce those methods and explain this integration. We end this introduction with simple predictions as to the results of our modelling effort. \\ \vspace{2em}

@@

A wide range of socio-ecological methods have been used in general conservation planning (these are reviewed in more details in chapter 2). In this thesis, we focus on participatory mapping and scenario-based approaches. Participatory mapping involves leveraging the knowledge that stakeholders hold about the geography of their landscape, in order to achieve a community-driven objective  \citep{plieninger_assessing_2013}. Scenarios are a flexible approach to forecasting the range of possible futures in landscapes \citep{peterson_scenario_2003}. In this thesis, we derive simple land use change and conservation scenarios from the results of a participatory mapping workshop. We integrate those scenarios with connectivity modelling in combination with two “warming” scenarios (Baseline and RCP 8.5) and one “control” scenario (Historic). \\

Depending on the scenario, the model generates different forest change dynamics. The Historic scenario assumes no change in forest composition and stands as our control. While the baseline scenario assumes no further warming and status quo forest change dynamics, the RCP 8.5 scenario is one of the most severe climate change scenarios, and the trends observed in the baseline scenario are exacerbated \cite{ipcc_summary_2013}. We also derive two simple land use change scenarios: Business as usual (BAU) and Reforestation. Those two scenarios are meant to represent two extremes in land use change, and it is likely that the most probable trajectories for our landscape will be within those two boundaries. In combination with the climate scenarios, this brings our total scenario number to 6 (for chapter 1, as conservation scenarios are added in chapter 2). \\

@@

We can therefore derive different predictions as to how connectivity will be affected for each species under our model. Three main predictions can be made. First, under the BAU scenario, we can expect that our land use change model will simulate an decrease in connectivity change for our focal species. We can also expect connectivity to maintain itself under the Reforestation scenario. Finally. We can expect climate change to impact more strongly species that prefer coniferous  and mixed forest types. \\

This thesis has two chapters.  In the first chapter, we combined a connectivity model, using circuit theory, with a land use and climate change model that uses a combination of statistical modelling and MCMC-based simulations (Markov Chain Monte Carlo). In the second chapter, we ran a stakeholder workshop to derive conservation priorities and use those results as inputs to derive simple, community driven, alternative conservation scenarios. We also compare and contrast the results of these scenarios and discuss the importance of considering stakeholder inputs to produce a resilient network of protected areas. \\
}%
\Intro

>>>>

\vspace{1em}

@@

Connectivity conservation planning (CCP), refers to the enterprise that engages multiple actors such as academics, NGOs (Non-Governmental Organizations), governmental bodies at different scales and in a common goal to conserve and restore the ecological connectivity of the landscape. CCP methods usually involve modelling the connectivity of the landscape of interest and using a prioritization method to determine conservation priorities, and modify land use practices to conserve or improve connectivity. In the following, we introduce connectivity modelling. We then introduce the study region and describe previous CCP and research. We then introduce the two other key concepts of the thesis: land use change modelling and participatory methods. \\ \vspace{2em}

@@

@@

Next we introduce those methods and explain this integration. We end this introduction with simple predictions as to the results of our modelling effort. \\ \vspace{2em}

@@

A wide range of socio-ecological methods have been used in general conservation planning (these are reviewed in more details in chapter 2), including participatory mapping. Participatory mapping involves leveraging the knowledge that stakeholders hold about the geography of their landscape, in order to achieve a community-driven objective  \citep{plieninger_assessing_2013}. Scenarios are a flexible approach to forecasting the range of possible futures in landscapes \citep{peterson_scenario_2003}.\\ \vspace{2em}

\subsection*{\textit{Thesis goals and expectations\\ \vspace{1em}}}
%%% EN CHANTIER

In this thesis, we attempt to remedy the two limitations mentionned above, in the context of an ongoing CCP effort in Montérégie, in southern Québec. We remedy to them in two separate chapters. \\
In the first chapter, we aimed to:
\begin{enumerate}
  \item Combine a connectivity model using circuit theory with a land use and climate change model.
  \item Model land use change by combining statistical modelling and MCMC-based (Markov Chain Monte Carlo) simulations.
  \item Derive two simple land use change scenarios: Business as usual (BAU) and Reforestation, meant to represent two extremes in land use change (the most probable trajectories for our landscape will be within those two boundaries).
  \item Contrast the changes in connectivity under both scenarios for our 5 umbrella species using circuit theory and feature detection methods. \\
\end{enumerate}
In the second chapter, we aimed to:
\begin{enumerate}
  \item Indentify connectivity conservation priorites in our study region as understood by local stakeholders using a participatory mapping method
  \item Use the results as inputs to derive simple, community driven, alternative conservation scenarios
  \item Contrast the changes in connectivity under these scenarios for our 5 umbrella species using circuit theory and feature detection methods.
  \item Discuss the importance of considering stakeholder inputs to produce a resilient network of protected areas. \\
\end{enumerate}

% Predictions // Expectations?

This thesis makes use of a hybrid modeling approach. We combine a model with scenarios which were derived from participatory methods. We integrate those scenarios with connectivity modelling in combination with two “warming” scenarios (Baseline and RCP 8.5) and one “control” scenario (Historic). Depending on the scenario, the model generates different forest change dynamics. The Historic scenario assumes no change in forest composition and stands as our control. While the baseline scenario assumes no further warming and status quo forest change dynamics, the RCP 8.5 scenario is one of the most severe climate change scenarios, and the trends observed in the baseline scenario are exacerbated \cite{ipcc_summary_2013}. \\

@@

We can therefore derive different predictions as to how connectivity will be affected for each species under our model. Three main predictions can be made. First, under the BAU scenario, we can expect that our land use change model will simulate an decrease in connectivity change for our focal species. We can also expect connectivity to maintain itself under the Reforestation scenario. Finally. We can expect climate change to impact more strongly species that prefer coniferous and mixed forest types. 
}%
\Intro
